---
title: "Analysis of football player performnace"
output: html_notebook
author: "Karan Bhatt"
---

Installing the necessary packages that we are using.
```{r}
install.packages("dpylr")
install.packages("ggplot2")
install.packages("gridExtra")
install.packages("moments")
install.packages("corrplot")
install.packages("ggcorrplot")
install.packages("caTools")
install.packages("caret")
install.packages("car")
install.packages("Metrics")
install.packages("DataExplorer")
install.packages("maps")
install.packages("plotly")
install.packages("randomForest")

```
Importing useful libraries
```{r}
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(moments)
library(corrplot)
library(ggcorrplot)
library(MASS)
library(caTools)
library(caret)
library(car)
library(Metrics)
library(tidyverse)
library(DataExplorer)
library(magrittr)
library(maps)
library(plotly)
library(randomForest)

```
Importing the dataset 
```{r}
df <- read_csv("D:/LSBU/Statistical Analysis Modeling/Dataset/archive/fifa_eda_stats.csv", locale = locale(encoding = "UTF-8"))
View(df)
head(df)
```
checking the dimention of data frame
```{r}
dim(df)
```
Removing the unnecessary columns for analysis
```{r}
df1 <- df [,-c(14,15,16,17,18,19,20,57)]
View(df1)
head(df1)
```
checking the dimesion of new dataframe
```{r}
dim(df1)
#make.names(names(df1))
#head(df1)
```
Checking total number of missing observation
```{r}
introduce(df1)
plot_intro(df1)
```
checking total number of  missing observation column and also checking null values 
```{r}
sum(is.na(df1))
sum(is.null(df1))
```
Removing the missing observation and storing in new data frame
```{r}
df2 <- na.omit(df1)
head(df2)
sum(is.na(df1))
sum(is.na(df2))
```
Stirng manipulation for value and wage column
```{r}
df2$Wage = gsub("€","",df2$Wage)
df2$Wage = as.numeric(gsub("K","",df2$Wage))
df2$Value = gsub("€","",df2$Value)
df2$Value = as.numeric(gsub("M","",df2$Value))
head(df2)
df3<-df2
head(df3)
```
Showing the summary of dataframe
```{r}
str(df3)
```
Showing the summary of data set
```{r}
summary(df3)
```

Showing wage of per season
```{r}
graph1 <- ggplot(data = df3[1:10,],aes(x=Name,y=Wage)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle= 90,size = 10,hjust =1)) +  labs(title = "Players/Season Wage") + 
  ylab("Wage") + 
  xlab("Players Name")
graph1

```
Now showing the age of players ranges in between
```{r}
graph2 <-(ggplot(df3,aes(x=Age)) + geom_bar() +   theme(axis.text.x = element_text(angle = 90,size = 10,hjust = 1)) +lims(x = c(NA,40)))
suppressWarnings(print(graph2))
```
Showing the prefered foot of players
```{r}
graph3 <- ggplot(df3,aes(x=`Preferred Foot`)) + geom_bar() + theme(axis.text.x = element_text(angle = 90,size = 10,hjust = 1))
graph3
```
Showing the highest players value ranges
```{r}

graph4 <- ggplot(df3,aes(x=`International Reputation`)) + geom_bar(color="red",fill="red") + theme(axis.text.x = element_text(angle = 90,size = 10))  + coord_flip()

graph4
```
Showing the skewness of the data in overall column 
```{r}
hist(df3$Overall,main="Skewness", xlab="Overall")
skewness(df3$Overall)
```
Check the variable 
```{r}
boxplot(df3$Overall)
```

showing the density plots of some data
```{r}
g_d = ggplot(data=df3,aes(x=Overall)) + geom_density(fill="blue",color="red")
g_d1 = ggplot(data=df3,aes(x=Crossing)) + geom_density(fill="blue",color="red")
g_d2 = ggplot(data=df3,aes(x=Finishing)) + geom_density(fill="blue",color="red")
g_d3 = ggplot(data=df3,aes(x=Wage)) + geom_density(fill="blue",color="red")
```
Printing the plots together
```{r}
g_d
g_d1
g_d2
g_d3

```
Finding the correlation between the 
```{r}
cor_df <- cor(df3[,unlist(lapply(df3, is.numeric))])
head(round(cor_df,2))

```
Finding any significance difference between left or right preffered foot
```{r}
xt1 <- df3 %>% filter(`Preferred Foot` == "Left") %>% select(`Skill Moves`) %>% pull()
xt2 <- df3 %>% filter(`Preferred Foot` == "Right") %>% select(`Skill Moves`) %>% pull()
yt1 <- df3 %>% filter(`Preferred Foot` == "Left") %>% select(`Finishing`) %>% pull()
yt2 <- df3 %>% filter(`Preferred Foot` == "Right") %>% select(`Finishing`) %>% pull()
xht <- wilcox.test(xt1, xt2, alternative = "two.sided")
yht <- wilcox.test(yt1, yt2, alternative = "two.sided")
xht
yht
```
Removing some more columns
```{r}
colnames(df3)
df4 <- df3[,-c(1,2,3,4,7,8,9,10,14,15)]
dim(df4)
colnames(df4)
```
Splitiing the data
```{r}
sum(is.na(df4))
train_r <- df4[1:12000,]
test_r <- df4[12001:17918,]
dim(train_r)
dim(test_r)
```
Applying multilinear regression
```{r}
train <- lm(train_r$Overall ~ .,data = train_r)
summary(train)
```
plotting the model
```{r}
plot(train)
```

 Now predict the value with model
```{r}

yp <- predict(train,test_r)
View(yp)
predict_value <- yp
p_v_d <- data.frame(predict_value=yp,actual=test_r$Overall)
dim(p_v_d)
View(p_v_d)
```
chekcing the rmse value of model
```{r}
data.frame(RMSE = RMSE(yp, test_r$Overall))
```
plotting the regression model
```{r}
avPlots(train)
```
```{r}


```
 k-fold cross validation
 checking the dimension of training dataset before applying cross validation
```{r}
dim(train_r)
```
 
```{r}
valid <- trainControl(method = "cv", number = 3)
```
```{r}
cross_model <- train(Overall ~ ., data = test_r, method = "lm", trControl = valid)
print(cross_model)
```
Applying the second model which is random forest
```{r}
train1 <- randomForest(x=train_r,y=train_r$Overall, ntree=200,type="regression")
train1
```

predicting the value from the train model
```{r}
yp1 <- predict(train1,test_r)
View(yp1)
p_v_d1 <- data.frame(predict_value=yp1,actual=test_r$Overall)
dim(p_v_d1)
View(p_v_d1)
```
checking the validation of random forest
```{r}
data.frame(RMSE = RMSE(yp1, test_r$Overall))

```
plotting the random forest model
```{r}
plot(train1)
varImpPlot(train1)
```
